---
output: 
  html_document: 
    keep_md: yes
---
---
### foofactors package

The `foofactors` package has 3 functions and this is a demo of how the functions work.

```{r}
#install_github("jokagyeman/foofacotrs")
library(foofactors)
```

#`fbind()`

##Description
The first function is `fbind` which puts two factors together as one.

```{r}
#Here is an example,

fbind(iris$Species[c(1,51,101)], PlantGrowth$group[c(1,11,21)])
```


#`freq_out()`

##Description
The second function is `freq_out`, which gives you a dataframe with factors and their frequency.

```{r}
# Here is an example

freq_out(iris$Species)

```


#`f_keep()`

##Description
The third function is `f_keep`, which prints factor levels as they are in the r object.

```{r}
# Here is an example

sons <- factor(c("John", "Caleb", "Joel"))

f_keep(sons)
```


#`f_nchar()`

##Description
This function counts the length of factor level names and prints it in a table arrange in descending order.

```{r}
# Here is an example

Subjects <- factor(c("Mathematics", "Statistics", "English", "French"))

f_nchar(Subjects)


```
